---
title: "Guidelines"
author: "Diana Da In Lee"
date: "2023-08-05"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
library(tidyverse)
library(dplyr)
library(magrittr)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
knitr::opts_chunk$set(echo = TRUE)
```

This guideline walks through how to implement the proposed hybrid approch to ethnoracial prediction in Lee, Diana, and Yamil Velez. "[Measuring descriptive representation at scale: Methods for predicting the race and ethnicity of public officials.](https://osf.io/tpsv6/)" (2023+).

We will use the following example data: 

```{r echo = F}
load('data/demo.rdata')
head(demo)
```
## 1. Image-Based Prediction

### 1.1. Collect Images

Collect profile images of the individuals in the dataset, using their first and last names as a keyword. Users may use any public engine. We provide a demo python code `collect_img.py` that allows for users to collect images from [DuckDuckGo](https://duckduckgo.com). 

The function automatically 1) removes images with no faces; 2) removes images with multiple faces; and 3) de-dupes identical faces (remove one of the images that are detected to be of a same person as the one in another image).

The `search` function in `collect_img.py` takes four arguments:

* `fullname`: First and last name to be used as a keyword for image search.
* `code`: Suffix of the jpeg filename to be used. Files will be saved with the naming convention "[code]_[1 through maxnum].jpg"
* `maxnum`: Total number of images you want to collect per keyword.
* `imgfolder`: Name of the folder you want the images to be saved.
* `detector`: Image prediction detector. Choose from `opencv`, `ssd`, `mtcnn`, `dlib`, `retinaface`, `mediapipe`, `yunet`, and `yolov8`. For differences across the detector, see [https://github.com/serengil/deepface](https://github.com/serengil/deepface).

### 1.2. Generate Predictions

Many different CNN models are available. Here, we demonstrate our method using `deepface` (https://github.com/serengil/deepface), which is implemented in Python.


## 2. Surname-Based Prediction

This part is very simple. Use `wru` package created by [Imai and Khanna (2016)](https://imai.fas.harvard.edu/research/race.html) to generate surname-based predictions:

```{r}
library(wru)
demo <- predict_race(voter.file = demo, surname.only = T)
demo <- demo %>% rename_at(vars(matches('^pred')), ~ gsub('pred', 'bayes', .x))
```

## Run multinomial logistic regression

```{r}
library(nnet)
#mod <- multinom(race ~ img.whi + img.bla + img.his + img.asi + bayes.whi + bayes.bla + bayes.his + bayes.asi + bayes.oth, data = demo)
#demo$pred_race = predict(mod, newdata = demo, "class")
```



Users are free to employ fancier machine learning algorithms (but our validation finds that this simple multinomial model performs just as well).