---
title: "Step-by-Step Guidelines to Implement Hybrid Ethnoracial Prediction"
author: "Diana Da In Lee (dl2860@columbia.edu)"
date: "Last Updated: `r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

```{r setup, include=FALSE}
rm(list=ls())
library(tidyverse)
library(dplyr)
library(magrittr)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
```

This guideline walks through how to implement the proposed hybrid approach to ethnoracial prediction in Lee, Diana, and Yamil Velez. "[Measuring descriptive representation at scale: Methods for predicting the race and ethnicity of public officials.](https://osf.io/tpsv6/)" (2023+).

We will use the US local elections dataset compiled by [de-Benedictis Kessner et al (2023)](https://dash.harvard.edu/handle/1/37373139). We've sampled 100 elections from the main dataset with 30\% of the names with verified ethnoracial information: 

```{r echo = F}
load('data/demo.rdata')
head(demo)
```

## 1. Image-Based Prediction

We first want to collect images associated with each name and make predictions based on the images. We provide two python functions `img_search` and `img_pred` to do these steps. For users who don't have python installed in their computer, we also provide a Google Colab demonstration here: [PredEthnorace_Demo.ipynb](https://github.com/DianaDaInLee/PredEthnorace/blob/main/PredEthnorace_Demo.ipynb).  

### 1.1. Collect Images

Collect profile images of the individuals in the dataset, using their first and last names as a keyword. Users may use any public engine. We provide a python function `img_search` (in `img_pred.py`) that allows for users to collect images from [DuckDuckGo](https://duckduckgo.com). The function automatically 1) removes images with no faces; 2) removes images with multiple faces; and 3) de-dupes identical faces (remove one of the images that are detected to be of a same person as the one in another image).

The `img_search` function in takes the following arguments:

* `fullname` (string): First and last name to be used as a keyword for image search.
* `maxnum` (integer): Total number of images you want to collect per keyword.
* `imgfolder` (string): Name of the folder you want the images to be saved. It will automatically create the folder in your working directory.

Each image will be saved in jpg as [`keyword`]_[0 through `maxnum`].jpg. All images associated with each keyword will be stored in its own folder named after the keyword (so make sure to dedup the full names in your dataset!). 

```{python, eval = F}
img_search(fullname = 'diana lee', maxnum = 3, imgfolder = 'demo')
glob.glob('demo/*/*')
```
````{python, eval = F}
['demo/diana_lee/diana_lee_0.jpg',
 'demo/diana_lee/diana_lee_1.jpg',
 'demo/diana_lee/diana_lee_2.jpg']
````

### 1.2. Generate Predictions

We provide a python function `img_pred` (in `img_pred.py`) that allows for users to predict ethnorace for each image using `deepface` developed by [Sefik Serengil](https://github.com/serengil/deepface) that uses a pre-trained CNN model [VGG-Face](https://sefiks.com/2018/08/06/deep-face-recognition-with-keras/) to predict ethnorace from an image. This package is available in python and is fairly straightforward to use. 

The `img_pred` function takes the following arguments:

* `imgfolder` (string): Name of the folder where the images are saved. Should be the same as the folder name used in `img_search`.
* `subfolder` (string): Name of a particular subfolder (i.e., keyword) under `imgfolder` that you want predictions to be performed. Default is NULL, which will generate predictions for all images in all subfolders saved in `imgfolder`.
* `det` (string): face detector backend to opencv (default), retinaface, mtcnn, ssd, dlib, mediapipe or yolov8. See [https://github.com/serengil/deepface](https://github.com/serengil/deepface) for differences across different detectors.
* `out_csv` (boolean): Save the result as a csv file to a `imgfolder`. Default is TRUE.

```{python, eval = F}
pred = img_pred(imgfolder = 'demo', subfolder = 'diana_lee', det = "opencv", out_csv = True)
pred
```
```{r, eval = F, echo = F}
pred <- read.csv('data/img_pred.csv')
pred
```

Not that there are many many different CNN models available. Our function is merely a demonstration using one of these models.

### 1.3 All at Once

For large dataset with many names, loop it!

```{python, eval = F}
# Python
import pyreadr
df = pyreadr.read_r('demo.rdata') 
demo = df["demo"]

# Collect Images
for index, row in demo.iterrows():
    print(row['fullname'])
    img_search(fullname = row['fullname'], maxnum = 3, imgfolder = 'demo')
    
# Generate Predictions
img_pred(imgfolder = 'demo', det = "opencv", out_csv = True)
```
```{r}
# R
# Merge It with Raw Data
pred <- read.csv('demo/img_pred.csv') %>%
  separate(fn, c('imgfolder', 'keyword', 'filenmae'), sep = '/') %>%
  select(asian:latino.hispanic, keyword) %>%
  rename_at(vars(asian:latino.hispanic), ~ paste0('image.', .x))
demo <- left_join(demo %>% mutate(keyword = tolower(gsub(" ", "_", fullname))), pred)
```

## 2. Surname-Based Prediction

This part is very simple. Use `wru` package created by [Imai and Khanna (2016)](https://imai.fas.harvard.edu/research/race.html) to generate surname-based predictions:

```{r, message = FALSE, comment = FALSE, warning = FALSE}
library(wru)
demo <- predict_race(voter.file = demo, surname.only = T)
demo <- demo %>% rename_at(vars(matches('^pred')), ~ gsub('pred', 'bayes', .x))
head(demo)
```

## 3. Run multinomial logistic regression

```{r}
library(nnet)
#mod <- multinom(race ~ img.whi + img.bla + img.his + img.asi + bayes.whi + bayes.bla + bayes.his + bayes.asi + bayes.oth, data = demo)
#demo$pred_race = predict(mod, newdata = demo, "class")
```

Users are free to employ fancier machine learning algorithms (but our validation finds that this simple multinomial model performs just as well).